---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# climr2 R package
### Written by Keefe Murphy

<!-- badges: start -->
<!-- badges: end -->

## Description

__climr2__ is an R package which downloads the latest climate data from NASA at monthly, quarterly, and yearly intervals, performs basic modelling of said data, and creates nice plots of temperature anomalies over time. Three functions are provided:

  1. `load_climr()`: for loading in the data at different intervals in a tidy format,
  
  2. a `fit()` method: for fitting statistical models (linear regression, LOESS, or smoothing splines) to said data,
  
  3. and a `plot()` method for producing nice visualisations based on `ggplot2`.
  
Typically, these functions are applied sequentially. This vignette aims to demonstrate a typical workflow of the `climr2` package.

## Installation

You can install the development version of `climr2` from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("Keefe-Murphy/climr2")
```

## Example

This is a basic example which shows you how to fit a smoothing spline to monthly southern hemisphere climate data:

```{r example}
library(climr2)

model <- fit(load_climr(type = "SH"), 
             data_type="monthly", 
             fit_type="smooth.spline")
```

Subsequently, a nice `ggplot2` plot can be created.

```{r example2}
p <- plot(model)
```

A more thorough introduction is provided in the `climr2` vignette.
